Polyglots: Crossing Origins by Crossing Formats

### 2013-08-26 main.tex
Final tidying up and images revert

%1 pages
\section{Introduction}
\label{sec:intro}
Web application security is concerned with protecting information as
it is manipulated by web applications. This is an important area
because ``attacks against web
applications constitute more than 60\% of the total attack attempts
observed on the Internet''~\cite{SANS09}.

@@

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{scenario.pdf}
  \caption{Overview of the scenario}
  \label{fig:scenario}
\end{figure}

@@

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{injection-scenario.pdf}
  \caption{Syntax injection scenario}
  \label{fig:injection-scenario}
\end{figure}

@@

\paragraph{Scenario}
The content smuggling scenario proceeds as illustrated in Figure~\ref{fig:scenario}.
Similarly to the previous scenarios, the victim is an authenticated user of a targeted vulnerable web site, \emph{vulnerable.com}. 
To give more context to the scenario, \emph{vulnerable.com} can be a cloud storage service. 
The target is infiltrated by the attacker (1), who uploads a polyglot to the web site. 
The polyglot is verified to be benign under the assumption that it belongs an allowed file type.
%The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
While still authenticated to \emph{vulnerable.com}, 
the victim visits the attackers web site, \emph{attacker.com} (2).
The \emph{attacker.com} site embeds the polyglot from \emph{vulnerable.com} (3), which is served as the benign type, but 
coerced to be interpreted as the malicious content type by the plug-in (4). 
The malicious format of the embedded 
polyglot is activated and a possible payload is to extract all the files stored in the victims account.

@@

%\begin{figure}[t]
%  \center
%  \includegraphics[width=0.49\textwidth]{smuggling-scenario.png}
%  \caption{Content smuggling scenario}
%  \label{fig:smuggling-scenario}
%\end{figure}

@@

@@

      l.addEventListener('complete', 
        function():void {
          u = 'attacker.com/?' + r.data;
          r = new URLRequest(u);
          l = new URLLoader(r);
        });
    }
  }
}
\end{lstlisting}

\begin{lstlisting}[label=lst:crossdomain, caption=Allow-all crossdomain.xml]
<?xml version="1.0"?>
<cross-domain-policy>
  <allow-access-from domain="*" />
</cross-domain-policy>
\end{lstlisting}

@@

\begin{table}[h!]
\begin{tabular}{l|c|c|c}
& object & embed & Adobe is default \\ \hline
Firefox & Yes & Yes & Yes \\ \hline
Chrome & Yes & Yes & No \\ \hline
Safari & Yes & Yes & Yes \\ \hline
Opera & Yes & Yes & Yes \\ \hline
Internet Explorer & No & Yes & Yes %\\ \hline
\end{tabular}
\caption{Comparison of browsers}
\label{tab:comparison}
\end{table}
%\subsection{Bypassing content filters}

>>>>

\vfill\eject
%1 pages
\section{Introduction}
\label{sec:intro}
Web application security is concerned with protecting information as
it is manipulated by web applications. This is an important area
because ``attacks against web
applications constitute more than 60\% of the total attack attempts
observed on the Internet''~\cite{SANS09}.

@@

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{scenario.png}
  \caption{Overview of the scenario}
  \label{fig:scenario}
\end{figure}

@@

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{injection-scenario.png}
  \caption{Syntax injection scenario}
  \label{fig:injection-scenario}
\end{figure}

@@

\paragraph{Scenario}
The content smuggling scenario proceeds as illustrated in Figure~\ref{fig:smuggling-scenario}.
Similarly to the previous scenarios, the victim is an authenticated user of a targeted vulnerable web site, \emph{vulnerable.com}. 
To give more context to the scenario, \emph{vulnerable.com} can be a cloud storage service. 
The target is infiltrated by the attacker (1), who uploads a polyglot to the web site. 
The polyglot is verified to be benign under the assumption that it belongs an allowed file type.
%The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
While still authenticated to \emph{vulnerable.com}, 
the victim visits the attackers web site, \emph{attacker.com} (2).
The \emph{attacker.com} site embeds the polyglot from \emph{vulnerable.com} (3), which is served as the benign type, but 
coerced to be interpreted as the malicious content type by the plug-in (4). 
The malicious format of the embedded 
polyglot is activated and a possible payload is to extract all the files stored in the victims account.

@@

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{smuggling-scenario.png}
  \caption{Content smuggling scenario}
  \label{fig:smuggling-scenario}
\end{figure}

@@

\vfill\eject

@@

      l.addEventListener('complete', 
        function():void {
          u = 'attacker.com/?' + r.data;
          r = new URLRequest(u);
          l = new URLLoader(r);
        });
}}}
\end{lstlisting}

\begin{lstlisting}[label=lst:crossdomain, caption=Allow-all crossdomain.xml]
<cross-domain-policy>
  <allow-access-from domain="*" />
</cross-domain-policy>
\end{lstlisting}

@@

\begin{table}[t]
\begin{tabular}{l|c|c|c}
& object & embed & Adobe is default \\ \hline
Firefox & Yes & Yes & Yes \\ \hline
Chrome & Yes & Yes & No \\ \hline
Safari & Yes & Yes & Yes \\ \hline
Opera & Yes & Yes & Yes \\ \hline
Internet Explorer & No & Yes & Yes %\\ \hline
\end{tabular}
\caption{Comparison of browsers}
\label{tab:comparison}
\end{table}
%\subsection{Bypassing content filters}
